The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-24 paper/ms.tex
more structure

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect $M$~new eclipsing binaries, and solar-like oscillations in $N$~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

@@

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.

>>>>

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and solar-like oscillations in \textcolor{red}{$N$}~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

@@

In this Section we will discuss the methods used for characterizing our new benchmark stars. We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.

@@

\section{Asteroseismology}
\label{asteroseismology}

\textcolor{red}{Guy - can you describe your pipeline here?}

@@

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.
